Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-20 paper/table_differential.tex
pass on evaluation
pass on numbers

\begin{table}[t]
  \small
  \vspace{-3ex}
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \setlength{\tabcolsep}{2pt}
  \renewcommand{\arraystretch}{0.95}
  \begin{tabular}{rcccccc}
    \toprule
    Issue\# \Comment{ & Date} & Fuzzer & Engine  & Status \Comment{&
    \multicolumn{1}{c}{Url}}  & Severity & Priority & Suite \\
    \midrule
    1  \Comment{& 4/12} & radamsa & \chakra{}   & \textbf{Fixed}  \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}}
    & 2 & \textbf{\lo} & \jsc{} \\ 
    2  \Comment{& 4/12} & radamsa & \chakra{}   & WontFix  \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}}
    & - & \hi{} & \jsc{} \\
    3  \Comment{& 4/14} & radamsa & \jsc{}  & New \Comment{&
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}}
    } & -  & \hi{} & \jsc{}    \\
    4  \Comment{& 4/25} & radamsa & \chakra{}  & \textbf{Fixed}     \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}}
    & 2 & \hi{} & \jerry{}   \\
    5  \Comment{& 4/29} & radamsa & \jsc{}  & \textbf{Fixed}  \Comment{&
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}}
    } & 2  & \hi{}  & \jerry{}\\

@@

    15 \Comment{& 8/21}  & radamsa & \chakra{} & \textbf{Confirmed} \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}}
    & - & \hi{} & Test262\\

@@

    19 \Comment{& 8/24}  & quickfuzz & \chakra{} & New \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}}
    & - & \hi{} & Test262\\

>>>>

\begin{table}[t]
  \small
  \vspace{-3ex}
  \centering
  \caption{List of bugs reports from Differential Testing.}
  \label{tab:bugs}
  \setlength{\tabcolsep}{1.5pt}
%  \renewcommand{\arraystretch}{0.95}
  \begin{tabular}{rcccccc}
    \toprule
    Issue\# \Comment{ & Date} & Fuzzer & Engine  & Status \Comment{&
    \multicolumn{1}{c}{Url}}  & Severity & Priority & Suite \\
    \midrule
    1  \Comment{& 4/12} & radamsa & \chakra{}   & \textbf{Fixed}  \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4978}{\#4978}}}
    & 2 & \textbf{\lo} & \jsc{} \\ 
    2  \Comment{& 4/12} & radamsa & \chakra{}   & WontFix  \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/4979}{\#4979}}}
    & - & \hi{} & \jsc{} \\
    3  \Comment{& 4/14} & radamsa & \jsc{}  & New \Comment{&
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}}
    } & -  & \hi{} & \jsc{}    \\
    4  \Comment{& 4/25} & radamsa & \chakra{}  & \textbf{Fixed}     \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5038}{\#5038}}}
    & 2 & \hi{} & \jerry{}   \\
    5  \Comment{& 4/29} & radamsa & \jsc{}  & \textbf{Fixed}  \Comment{&
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}}
    } & 2  & \hi{}  & \jerry{}\\

@@

    15 \Comment{& 8/21}  & radamsa & \chakra{} & \textbf{Fixed} \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5617}{\#5617}}}
    & 3 & \hi{} & Test262\\

@@

    19 \Comment{& 8/24}  & quickfuzz & \chakra{} & \textbf{Confirmed} \Comment{&
    \anonym{\href{https://github.com/Microsoft/\chakra{}Core/issues/5630}{\#5630}}}
    & 2 & \hi{} & Test262\\
